The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-03-23 RET_Hosts_IR.tex
Updates from Overleaf

There are a limited number of events detected in the local Universe whose properties are consistent with the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Perley2019}. The transient declined from its discovery, with constraints on a ~1 day rise time, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova \replylluis{(KN; \citealt{Ho2019})}. There are myriad explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova \replylluis{(CEJSN; \citealt{Soker2019})}; \replychris{or a wind-driven transient \citep{Uno2020}}.
Other nearby rapid transients include the local fast-declining SN-like transient \citep{McBrien2019} which is explained by the destruction of a white dwarf, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.  It is currently unclear whether these transients do indeed represent the local analogues of the DES and PS RETs.

@@

DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.64792 &      OzDES &       6.58333 \\
DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.19647 &      OzDES &      10.16667 \\

@@

DES13S2wxf     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.56985 &      OzDES &       5.41639 \\
DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.58236 &      OzDES &       4.00000 \\

@@

DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.71205 &      OzDES &      45.50000 \\
DES13X3gmd     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.78082 &      OzDES &      13.91667 \\

@@

DES13X2wvv     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.47503 &      OzDES &       4.50000 \\

@@

DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.05211 &      OzDES &       0.75000 \\

@@

DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.82982 &      OzDES &       3.50000 \\

@@

DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.44739 &      OzDES &       2.33333 \\

@@

DES15S1fll     & 42.78846 &  -0.19747 & $20.95 \pm 0.03$ & 0.22647 &      OzDES &       0.66667 \\

@@

DES14X3pkl     & 37.21103 &  -4.80741 & $22.40 \pm 0.06$ & 0.29537 &      OzDES &       5.16667 \\
DES13X3npb     & 36.64218 &  -4.13381 & $20.79 \pm 0.05$ & 0.49542 &      OzDES &       5.16667 \\
DES15X2ead     & 36.48913 &  -6.45118 & $20.08 \pm 0.03$ & 0.23175 &      OzDES &       2.00000 \\

@@

DES14S2plb     & 41.85667 &  -1.61811 & $18.38 \pm 0.03$ & 0.11531 &      OzDES &       2.00000 \\
DES14S2pli     & 41.22837 &  -1.09830 & $20.86 \pm 0.03$ & 0.35478 &      OzDES &       3.41667 \\

@@

DES14C3tnz     & 52.86248 & -28.51318 & $22.26 \pm 0.03$ & 0.70452 &      OzDES &       5.79361 \\
DES15X3mxf     & 36.74009 &  -5.23991 & $22.43 \pm 0.04$ & 0.43673 &      OzDES &       9.83333 \\

@@

DES15C3lpq     & 52.71204 & -28.61319 & $23.28 \pm 0.03$ & 0.61365 &      OzDES &       6.16667 \\

@@

DES15C3nat     & 52.88528 & -28.72370 & $23.39 \pm 0.03$ & 0.83929 &      OzDES &      18.62222 \\
DES15C3mgq     & 52.76901 & -28.20882 & $22.97 \pm 0.03$ & 0.23031 &      OzDES &       8.16667 \\
DES15E2nqh     &  9.73174 & -43.08707 & $23.29 \pm 0.03$ & 0.51525 &      OzDES &       6.83333 \\
DES15C3opk     & 51.66147 & -28.34737 & $23.05 \pm 0.03$ & 0.56984 &      OzDES &      12.16667 \\

@@

\begin{figure*}
\includegraphics[width=0.7\textwidth]{figs/RET_Mosaic.png}
\caption{Selection of DES RET host galaxies in an RGB composite of the DES $gri$ band deep coadds from \citet{Wiseman2020}. The locations of the transients are indicated with cyan crosses. The stamps have a size of 10\arcsec in each direction.
\label{fig:mosaic}}
\end{figure*}

@@

\section{Estimating host galaxy properties}
\label{sec:measure}
\subsection{Photometric stellar parameters \label{subsec:sedfit}}
To estimate the physical properties of the DES RET host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models. We simulate a suite of synthetic galaxy star-formation histories from which we synthesise model SEDs using stellar population models from \citet{Bruzual2003}  and a \citet{Chabrier2003} initial mass function (IMF).  The suite of models is drawn from the same distribution of parameters as used in \citet{Kauffmann2003} and similar papers \citep[e.g.][]{Gallazzi2005,Gallazzi2009} and closely follows the method of \citet{Childress2013}. From the synthetic SEDs we derive model magnitudes in the DES $griz$ bands and compare them to the observed \replylluis{Kron} magnitudes \replylluis{from the deep photometric catalogue of \citet{Wiseman2020}}. For each set of model and observed magnitudes we calculate a $\chi^2$ value, and from these calculate a PDF for key model parameters (mass-to-light ratio $M/L$, from which we derive $M_*$, and specific star-formation rate sSFR). To estimate uncertainties, we take the values at the 16th and 84th percentiles of the resulting PDF to be our $1\sigma$ lower and upper bounds. The results are presented in Table \ref{tab:derived}. \replylluis{These parameters are estimated using global photometry of the entire galaxies, and thus represent the overall stellar population characteristics.}

@@

To estimate parameters from the OzDES host galaxy spectra requires several processing steps. We first apply a flux calibration by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry (further details on the mangling process are provided in \citealt{Swann2020}). We use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres. \replylluis{This way the resulting spectrum is a more accurate representation of the true spectrum at that point in the galaxy. This only holds, however, for the area covered by the fibre and we note that the resulting spectrum is not necessarily representative of the galaxy as a whole. There are several reasons this measurement may differ from one made at the SN explosion site, such as metallicity and age gradients or structure such as bars and discs (see e.g. \citealt{Iglesias-Paramo2013,Iglesias-Paramo2016}). We proceed with our analysis with this caveat acknowledged.}

@@

Due to the redshift range of our sample, and the limited wavelength coverage of the spectra ($3000-8000$~\AA), we are unable to use a single line ratio to estimate the oxygen abundances. We thus determine a set of indicators for which to calculate abundances. For the O3N2 and N2 indicators we use the calibration of \citet{Pettini2004} (PP04), and if \SII~is detected we derive an abundance using the S2N2 diagnostic of \citet{Dopita2016}. For the R23 indicator, we use the calibration of \citet{Kobulnicky2004} (KK04). At abundances around $12 + \log \mathrm{(O/H)} \sim 8.4$, the R23 indicator becomes two-tailed, with a low and a high value of metallicity corresponding to a single R23 ratio. In cases where the lines are available, we break this degeneracy by cross-calibrating with the \NII/\OII~ratio \citep{Kewley2008}. In the cases where \NII~is not available, and there are no other diagnostics that can be used to inform the choice of branch, we use the host galaxy stellar mass to derive a crude metallicity estimate from the mass-metallicity relation (MZR) of \citet{Kewley2008} based upon the PP04 O3N2 diagnostic. For $12 + \log \mathrm{(O/H)}_{\mathrm{MZR}} < 8.4$ we chose the lower branch, while for higher MZR metallicities we choose the upper branch. \replychris{We note that this is a rough estimation}. If we leave the branch choice for those with no \NII~to be random, we find that the results are consistent to within uncertainties

@@

The comparison shows RET hosts to be shifted to higher sSFRs CCSNe. In 98\% of the posterior samples the RET sSFR distribution loc was at a higher value than SNe II, while the same was true 95\% of the time for RETs when comparing with SESNe. \phil{The mean difference is 0.6 dex. To test whether some of this could be attributed to the difference in redshift between the samples we apply a crude redshift correction based on the parameterisation of the SFMS at different redshifts by \citet{Salim2007} and \citet{Noeske2007}, as has been done in other comparisons such as \citet{Taggart2019}. Correcting all SFRs to $z=0$ would result in the CCSN SFRs droping by an average of 0.05 dex, while the RETs would drop 0.35 dex, i.e. a difference of 0.30 dex, or half of the observed difference. The remaining 0.3 dex is thus consistent with being an intrinsic difference.}   
RET host galaxies are significantly lower in sSFR than LGRBs. While the distributions are similar in shape, with a mean difference in scale of 0.28, the mean difference in loc is -1.64, with no overlap between the posterior distributions. The sSFR distribution of SLSNe hosts is heavily positively skewed (with alpha values of $5.54^{\scriptscriptstyle+1.8}_{\scriptscriptstyle-0.98}$ compared to $-0.18^{\scriptscriptstyle+0.75}_{\scriptscriptstyle-0.76}$ for RET hosts). The strong high-sSFR tail shows SLSNe \replychris{occur in a different galaxy} population to RETs.

@@

\section{Discussion}
\label{sec:disc}
\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/RET_vs_host.png}
\caption{RET lightcurve properties as a function of host galaxy measurements.
\label{fig:ret_v_host}}
\end{figure}
\subsection{Selection Biases \label{subsec:disc_bias}}
The properties presented in Section \ref{sec:analysis} are derived from a subset of the total sample of RETs. Of 106 objects, under half \replylluis{(52/106)} have secure host galaxy redshifts. Three of these were obtained from transient spectra, for which we are unable to disentangle the host and transient contributions, and four were obtained by programmes for which we do not have access to the spectra. Of the remaining 45, it was possible to derive a metallicity \replylluis{or at least a limmit} for 40 host galaxies, \replylluis{while five exceeded the redshift range for the necessary lines to fall within the wavelength coverage of AAOmega}. The observed metallicity distribution could have arisen if the galaxies without redshifts (and metallicities) are systematically higher in metallicity than those for which measurements were possible. For low SNR objects, redshifts are typically obtained from only two of the strongest lines (e.g. \halpha, \hbeta, \OIII, and \OII). \replylluis{It is likely that the redshifts were not obtained because the galaxies are physically smaller or are at higher redshift. However, galaxies with high metallicity have weaker \OIII~lines, meaning they are less likely to have a positive redshift detection compared to less enriched galaxies with the same mass and redshift. Future, deeper spectral observation programmes as well as large, complete low-redshift samples are necessary to eliminate this possible bias.}

Another possibility is that the hosts without a redshift are mostly non-starforming, passive galaxies, for which a redshift is typically harder to obtain than for emission-line galaxies \citep{Yuan2015,Childress2017,Lidman2020}. In order to test this possibility, we examined the RETs that do not have a host galaxy redshift. Table \ref{tab:z_cuts} shows the numbers of RETs that failed various stages of the redshifting process, and is summarised in Fig. \ref{fig:mag_dist}. Of the 48 objects without a redshift, 40 of them have host galaxies detected in the SN Deep coadds of \citet{Wiseman2020}. Of more significance is that only 34 have host galaxies in the SVA1 catalogues which were used for targetting during the OzDES campaign. The other, `hostless', objects are either transients that are located remotely from a galaxy that was detected, or are hosted by a galaxy that was not detected. Non-detected hosts are either intrinsically faint and thus low in mass, situated at high redshift, or both. Neither are expected to be systematically higher in metallicity than the detected hosts. Similarly, a further 16 hosts were detected but not targetted by OzDES, due to being too faint to pass the selection criteria ($m_r < 24.5$), leaving 18 that were targetted but no redshift was found. The resulting redshift completeness of targetted objects is 70\% (82\% for objects brighter than $m_r = 24$~mag, which is in line with the average for OzDES as a whole \citep{Lidman2020}.
In Fig. \ref{fig:g-i} we show the observer-frame $r$-band magnitudes and $g-i$ colours for all RET hosts that were detected. The 40 objects with detected hosts but no redshift lie at fainter magnitudes, and appear to extend to bluer colours than those with secure redshifts. This is contrary to the hypothesis that they are high-redshift and/or passive hosts, but instead are low-mass, star-forming galaxies whose line fluxes were not strong enough to be detected.

\begin{table}
    \centering
    \begin{tabular}{l|l}
         Cut &  Number of remaining objects \\
        \toprule
        All RETs & 106 \\
        No redshift   & 48\\
        Host in SN Deep & 40\\
        Host in SVA1 & 34 \\
        Targetted by OzDES & 18 \\
        \bottomrule
    \end{tabular}
    \caption{Numbers of RETs passing various cuts relating to redshift targetting.}
    \label{tab:z_cuts}
\end{table}

@@

\section{Conclusions}
\label{sec:conc}
By analysing the host galaxies of 49 rapidly evolving transients (RETs) discovered in the Dark Energy Survey, we have been able to place constraints on the nature of this as-yet unexplained phenomenon. We conclude that RETs are strongly linked to massive stars, due to their apparent reliance on star formation. Their origin is likely from more massive stars than SNe II, and perhaps all SESNe, as they require higher galaxies with sSFR. RET hosts are lower in metallicity than SNe II hosts, suggesting some reliance on rotational energy or other metallicity-dependent effects.
Of the RET analogues discovered in modern large-area, high-cadence surveys, ZTF18abvkwla shares the most similar host galaxy characteristics with the DES RET population. SN2018gep appears in a galaxy too faint to have been detected by DES-SN at the redshift of most of the DES RETs, while the host of AT2018cow is much higher in metallicity.

\replychris{While current surveys such as ZTF, GOTO, and BlackGEM are well equipped to find low-redshift RETs, a sample similar to that presented here will likely not be collected until LSST comes online. With several hundreds of objects, detailed studies of RETs and their hosts will be possible in a systematic and more complete manner as has been achieved with LGRBs and SLSNe. At that point, the conclusions of this paper will be able to be tested.}

@@

\replychris{To compare two distributions we follow the method outlined in \citet{Wiseman2020}. We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler (NUTS; \citealt{Hoffman2014}) Hamiltonian Monte Carlo algorithm via the  \texttt{pymc3}\footnote{https://docs.pymc.io/} package to explore the posterior distribution. We use a warm-up period of $5\times10^3$ iterations and a fit period of $10^4$ iterations. Fig. \ref{fig:histfit} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared. Each resulting distribution is described by the `loc' (location), `scale' (spread), and `alpha' (skewness). We then compare the differences in these parameters, as seen in Fig. \ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.} 
\twocolumn
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe II, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and LGRBs, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SLSNe, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}

\section{Bayesian Fits - Metallicity}
\label{app:c}
In this section, we present the Bayesian fits to the metallicity distributions of RETs and the comparison samples.
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_OH_histfit_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SESNe, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_OH_histfit_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SNe II, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_OH_histfit_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and LGRBs, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure}

>>>>

There are a limited number of events detected in the local Universe whose properties are consistent with the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Perley2019}. The transient declined from its discovery, with constraints on the rise time of 1 day, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova \replylluis{(KN; \citealt{Ho2019})}. There are many diverse explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova \replylluis{(CEJSN; \citealt{Soker2019})}; \replychris{or a wind-driven transient \citep{Uno2020}}.
Other nearby rapid transients include the local fast-declining SN-like transient SN2018kzr \citep{McBrien2019} which is explained by the destruction of a white dwarf, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.  It is currently unclear whether these transients do indeed represent the local analogues of the DES and PS RETs.

@@

DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.64792 &      OzDES &       6.6 \\
DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.19647 &      OzDES &      10.2 \\

@@

DES13S2wxf     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.56985 &      OzDES &       5.4 \\
DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.58236 &      OzDES &       4.0 \\

@@

DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.71205 &      OzDES &      45.5 \\
DES13X3gmd     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.78082 &      OzDES &      13.9 \\

@@

DES13X2wvv     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.47503 &      OzDES &       4.5 \\

@@

DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.05211 &      OzDES &       0.75 \\

@@

DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.82982 &      OzDES &       3.5 \\

@@

DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.44739 &      OzDES &       2.3 \\

@@

DES15S1fll     & 42.78846 &  -0.19747 & $20.95 \pm 0.03$ & 0.22647 &      OzDES &       0.67 \\

@@

DES14X3pkl     & 37.21103 &  -4.80741 & $22.40 \pm 0.06$ & 0.29537 &      OzDES &       5.2 \\
DES13X3npb     & 36.64218 &  -4.13381 & $20.79 \pm 0.05$ & 0.49542 &      OzDES &       5.2 \\
DES15X2ead     & 36.48913 &  -6.45118 & $20.08 \pm 0.03$ & 0.23175 &      OzDES &       2.0 \\

@@

DES14S2plb     & 41.85667 &  -1.61811 & $18.38 \pm 0.03$ & 0.11531 &      OzDES &       2.0 \\
DES14S2pli     & 41.22837 &  -1.09830 & $20.86 \pm 0.03$ & 0.35478 &      OzDES &       3.4 \\

@@

DES14C3tnz     & 52.86248 & -28.51318 & $22.26 \pm 0.03$ & 0.70452 &      OzDES &       5.8 \\
DES15X3mxf     & 36.74009 &  -5.23991 & $22.43 \pm 0.04$ & 0.43673 &      OzDES &       9.8 \\

@@

DES15C3lpq     & 52.71204 & -28.61319 & $23.28 \pm 0.03$ & 0.61365 &      OzDES &       6.2 \\

@@

DES15C3nat     & 52.88528 & -28.72370 & $23.39 \pm 0.03$ & 0.83929 &      OzDES &      18.6 \\
DES15C3mgq     & 52.76901 & -28.20882 & $22.97 \pm 0.03$ & 0.23031 &      OzDES &       8.1 \\
DES15E2nqh     &  9.73174 & -43.08707 & $23.29 \pm 0.03$ & 0.51525 &      OzDES &       6.8 \\
DES15C3opk     & 51.66147 & -28.34737 & $23.05 \pm 0.03$ & 0.56984 &      OzDES &      12.2 \\

@@

\begin{figure*}
\includegraphics[width=0.7\textwidth]{figs/RET_Mosaic.png}
\caption{Selection of DES RET host galaxies in an RGB composite of the DES $gri$ band deep coadds from \citet{Wiseman2020}. The locations of the transients are indicated with cyan crosses. The stamps have a size of 10\arcsec in each direction. \replylluis{DES17X1hjk is considered hostless.}
\label{fig:mosaic}}
\end{figure*}

@@

\section{Estimating host galaxy properties}
\label{sec:measure}
\subsection{Photometric stellar parameters \label{subsec:sedfit}}
To estimate the physical properties of the DES RET host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models. We simulate a suite of synthetic galaxy star-formation histories from which we synthesise model SEDs using stellar population models from \citet{Bruzual2003}  and a \citet{Chabrier2003} initial mass function (IMF).  The suite of models is drawn from the same distribution of parameters as used in \citet{Kauffmann2003} and similar papers \citep[e.g.][]{Gallazzi2005,Gallazzi2009} and closely follows the method of \citet{Childress2013}. From the synthetic SEDs we derive model magnitudes in the DES $griz$ bands and compare them to the observed \replylluis{Kron} magnitudes \replylluis{from the deep photometric catalogue of \citet{Wiseman2020}}. For each set of model and observed magnitudes we calculate a $\chi^2$ value, and from these calculate a PDF for key model parameters (mass-to-light ratio $M/L$, from which we derive $M_*$, and specific star-formation rate sSFR). To estimate uncertainties, we take the values at the 16th and 84th percentiles of the resulting PDF to be our $1\sigma$ lower and upper bounds. The results are presented in Table \ref{tab:derived}. \replylluis{These parameters are estimated using global photometry of the entire galaxies, and thus represent the overall stellar population.}

@@

To estimate parameters from the OzDES host galaxy spectra requires several processing steps. We first apply a flux calibration by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry (further details on the mangling process are provided in \citealt{Swann2020}). We use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres. \replylluis{The resulting spectrum is a more accurate representation of the true spectrum at that point in the galaxy. This only holds, however, for the area covered by the fibre and we note that the resulting spectrum is not necessarily representative of the galaxy as a whole. There are several reasons this measurement may differ from one made at the SN explosion site, such as metallicity and age gradients or structure such as bars and discs (see e.g. \citealt{Iglesias-Paramo2013,Iglesias-Paramo2016}). We proceed with our analysis with this caveat acknowledged.}

@@

Due to the redshift range of our sample, and the limited wavelength coverage of the spectra ($3000-8000$~\AA), we are unable to use a single line ratio to estimate the oxygen abundances. We thus determine a set of indicators for which to calculate abundances. For the O3N2 and N2 indicators we use the calibration of \citet{Pettini2004} (PP04), and if \SII~is detected we derive an abundance using the S2N2 diagnostic of \citet{Dopita2016}. For the R23 indicator, we use the calibration of \citet{Kobulnicky2004} (KK04). At abundances around $12 + \log \mathrm{(O/H)} \sim 8.4$, the R23 indicator becomes two-tailed, with a low and a high value of metallicity corresponding to a single R23 ratio. In cases where the lines are available, we break this degeneracy by cross-calibrating with the \NII/\OII~ratio \citep{Kewley2008}. In the cases where \NII~is not available, and there are no other diagnostics that can be used to inform the choice of branch, we use the host galaxy stellar mass to derive a crude metallicity estimate from the mass-metallicity relation (MZR) of \citet{Kewley2008} based upon the PP04 O3N2 diagnostic. For $12 + \log \mathrm{(O/H)}_{\mathrm{MZR}} < 8.4$ we chose the lower branch, while for higher MZR metallicities we choose the upper branch. \replychris{We note that this is a rough estimation}. If we leave the branch choice for those with no \NII~to be random, we find that the results are consistent to within uncertainties.

@@

The comparison shows RET hosts to be shifted to higher sSFRs CCSNe. In 98\% of the posterior samples the RET sSFR distribution loc was at a higher value than SNe II, while the same was true 95\% of the time for RETs when comparing with SESNe. \phil{The mean difference is 0.6 dex. To test whether some of this could be attributed to the difference in redshift between the samples we apply a crude redshift correction based on the parameterisation of the SFMS at different redshifts by \citet{Salim2007} and \citet{Noeske2007}, as has been done in other comparisons such as \citet{Taggart2019}. Correcting all SFRs to $z=0$ would result in the CCSN SFRs droping by an average of 0.05 dex, while the RETs would drop 0.35 dex, i.e. a difference of 0.30 dex, or half of the observed difference. The remaining 0.3 dex is thus consistent with being an intrinsic difference.}   
RET host galaxies are significantly lower in sSFR than LGRBs. While the distributions are similar in shape, with a mean difference in scale of 0.09, the mean difference in loc is -1.16, with no overlap between the posterior distributions. The sSFR distribution of SLSNe hosts is much broader than the RETs, with a scale of 1.12, twice that of the RETs. They are also shifted to higher sSFRs than RETs, with the loc of the distribution on average 0.76 dex greater than RETs. The strong high-sSFR tail shows SLSNe \replychris{occur in a different galaxy} population to RETs.

@@

\section{Discussion}
\label{sec:disc}
\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/RET_vs_host.png}
\caption{RET lightcurve properties as a function of host galaxy measurements.
\label{fig:ret_v_host}}
\end{figure}
\subsection{Selection Biases \label{subsec:disc_bias}}
The properties presented in Section \ref{sec:analysis} are derived from a subset of the total sample of RETs. Of 106 objects, under half \replylluis{(52/106)} have secure host galaxy redshifts. Three of these were obtained from transient spectra, for which we are unable to disentangle the host and transient contributions, and four were obtained by programmes for which we do not have access to the spectra. Of the remaining 45, it was possible to derive a metallicity \replylluis{or at least a limit} for 40 host galaxies, \replylluis{while five exceeded the redshift range for the necessary lines to fall within the wavelength coverage of AAOmega}. The observed metallicity distribution could have arisen if the galaxies without redshifts (and metallicities) are systematically higher in metallicity than those for which measurements were possible. For low SNR objects, redshifts are typically obtained from only two of the strongest lines (e.g. \halpha, \hbeta, \OIII, and \OII). \replylluis{It is likely that the redshifts were not obtained because the galaxies are physically smaller or are at higher redshift. However, galaxies with high metallicity have weaker \OIII~lines, meaning they are less likely to have a positive redshift detection compared to less enriched galaxies with the same mass and redshift. Future, deeper spectral observation programmes as well as large, complete low-redshift samples are necessary to eliminate this possible bias.}

Another possibility is that the hosts without a redshift are mostly non-starforming, passive galaxies, for which a redshift is typically harder to obtain than for emission-line galaxies \citep{Yuan2015,Childress2017,Lidman2020}. In order to test this possibility, we examined the RETs that do not have a host galaxy redshift. Table \ref{tab:z_cuts} shows the numbers of RETs that failed various stages of the redshifting process, and is summarised in Fig. \ref{fig:mag_dist}. Of the 57 objects without a redshift, 47 of them have host galaxies detected in the SN Deep coadds of \citet{Wiseman2020}. Of more significance is that only 40 have host galaxies in the SVA1 catalogues which were used for targetting during the OzDES campaign. The other, `hostless', objects are either transients that are located remotely from a galaxy that was detected, or are hosted by a galaxy that was not detected. Non-detected hosts are either intrinsically faint and thus low in mass, situated at high redshift, or both. Neither are expected to be systematically higher in metallicity than the detected hosts. Similarly, a further 22 hosts were detected but not targetted by OzDES, due to being too faint to pass the selection criteria ($m_r < 24.5$), leaving 18 that were targetted but no redshift was found. The resulting redshift completeness of targetted objects is 71\% (83\% for objects brighter than $m_r = 24$~mag), which is in line with the average for OzDES as a whole \citep{Lidman2020}.
In Fig. \ref{fig:g-i} we show the observer-frame $r$-band magnitudes and $g-i$ colours for all RET hosts that were detected. The 47 objects with detected hosts but no redshift lie at fainter magnitudes, and appear to extend to bluer colours than those with secure redshifts. This is contrary to the hypothesis that they are high-redshift and/or passive hosts, but instead are low-mass, star-forming galaxies whose line fluxes were not strong enough to be detected.

\begin{table}
    \centering
    \begin{tabular}{l|l}
         Cut &  Number of remaining objects \\
        \toprule
        All RETs & 106 \\
        No redshift   & 57\\
        Has host in SN Deep & 47\\
        Has host in SVA1 & 40 \\
        Targetted by OzDES & 18 \\
        \bottomrule
    \end{tabular}
    \caption{Numbers of RETs passing various cuts relating to redshift targetting and completeness. Each row is a subset of the row above.}
    \label{tab:z_cuts}
\end{table}

@@

\section{Conclusions}
\label{sec:conc}
By analysing the host galaxies of 49 rapidly evolving transients (RETs) discovered in the Dark Energy Survey, we have been able to place constraints on the nature of this as-yet unexplained phenomenon. We conclude that RETs are strongly linked to massive stars, due to their hosts all exhibiting signatures of star formation. They likely originate from stars more massive, on average, than than those that cause SNe II, and perhaps all SESNe, as they occur in galaxies with higher sSFR. RET hosts are significantly lower in metallicity than SN II hosts, and marginally lower than SESN hosts, suggesting some reliance on rotational energy or other metallicity-dependent effects.
Of the RET analogues discovered in modern large-area, high-cadence surveys, ZTF18abvkwla shares the most similar host galaxy characteristics with the DES RET population. SN2018gep appears in a galaxy too faint to have been detected by DES-SN at the redshift of most of the DES RETs, while the host of AT2018cow is much higher in metallicity.

\replychris{While current surveys such as ZTF \citep{Bellm2019}, GOTO \citep{Dyer2018}, and BlackGEM \citep{Bloemen2016} are well equipped to find low-redshift RETs, a sample similar to that presented here will likely not be collected until LSST comes online. With several hundreds of objects, detailed studies of RETs and their hosts will be possible in a systematic and more complete manner as has been achieved with LGRBs and SLSNe. At that point, the conclusions of this paper will be able to be tested.}

@@

\replychris{To compare two distributions we follow the method outlined in \citet{Wiseman2020}. We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler (NUTS; \citealt{Hoffman2014}) Hamiltonian Monte Carlo algorithm via the  \texttt{pymc3}\footnote{https://docs.pymc.io/} package to explore the posterior distribution. We use a warm-up period of $5\times10^3$ iterations and a fit period of $10^4$ iterations. Fig. \ref{fig:histfit_s12_ssfr} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared. Each resulting distribution is described by the `loc' (location), `scale' (spread), and `alpha' (skewness). We then compare the differences in these parameters, as seen in Fig. \ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.} 
\twocolumn
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe II, accounting for uncertainties in each bin.
\label{fig:histfit_ssfr_s13}}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and LGRBs, accounting for uncertainties in each bin.
\label{fig:histfit_ssfr_k15}}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SLSNe, accounting for uncertainties in each bin.
\label{fig:histfit_ssfr_p16}}
\end{figure}

\section{Bayesian Fits - Metallicity}
\label{app:c}
In this section, we present the Bayesian fits to the metallicity distributions of RETs and the comparison samples.
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_OH_histfit_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SESNe, accounting for uncertainties in each bin.
\label{fig:histfit_oh_s12}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_OH_histfit_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SNe II, accounting for uncertainties in each bin.
\label{fig:histfit_oh_s13}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_OH_histfit_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and LGRBs, accounting for uncertainties in each bin.
\label{fig:histfit_oh_k15}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_OH_histfit_final.png}
\caption{Results of the MCMC fits to the PDFs of metallicity for DES RETs and SLSNe, accounting for uncertainties in each bin.
\label{fig:histfit_oh_p16}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
